---
title: "Analysis of a dataset to compare different star classifications"
subtitle: ""
author: "Team JMAD <br> Alex, Declan, Jiayi and Malachi "
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)

```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
# Load your data here
ds <- read.csv("data/hygdata_v3.csv")
  
```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "img/cosmiccliffs.png"
)
```



class: inverse, center, middle

# Section 1 - Introduction

---

# Research Question


## To investigate the relationship between different properties of stars, especifically the relationship between Spectral class and Absolute magnitude.


---

# Stating and Refining the Research Question

--

- 1) Descriptive: ssummarize the frequency for each different spectral class from a dataset based on a collection of stars.

--

- 2) Exploratory: examine relationships between a range of different properties of stars.

--

- 3) Inferential: examine whether there are any trends between temperature and luminosity.

--

- 4) Predictive: predicting the apparent magnitude based on spectral class.


---

# Our Dataset

37 variables and 119,614 observations

```{r view-dataset, eval=TRUE, echo=FALSE}
glimpse(ds)
```



---
# Filtered Dataset

```{r echo=FALSE}
ds_hyd_clean <- ds %>%
  filter(distance > 0, distance < 100000) %>%
  subset(select = -c(hip, hd, hr, gl, bf, proper, ra, dec, pmra, pmdec, flam, x, y, z , vx, vy, vz, rarad, decrad, pmrarad, pmdecrad, bayer, var, var_min, var_max, rv, comp, comp_primary, con, base))  %>%
  rename (
    star_ID = id,
    apparent_magnitude = mag,
    luminosity = lum,
    absolute_magnitude = absmag,
    colour_index = ci,
    spectral_class = spect
  )



```
```{r eval=TRUE, echo=FALSE}
glimpse(ds_hyd_clean)
```

--

7 variables and 109,398 observations

--

- Categorical: spectral class
- Discrete: star ID
- Continuous: distance, apparent magnitude, absolute magnitude, colour index, luminosity

---

class: inverse, center, middle

# Section 2 - Data Analysis

---

# Method

--

Q1

- 1) Remove invalid observations 
- 2) Adding two new columns - main spectral class + sub spectral class 
- 3)Plot a bar chart

--

Q2

- 1) Plot a scatter/line graph
- 2) Facet the scatter/line graph

--

Q3

- 1) Plot a scatter/line graph

--

Q4

- 1) Split the dataset into 5 subsets
- 2) Make the logistic regression model: apparent magnitude <- absolute magnitude + distance

---

# The Plots and Findings



---

# The Models and Findings
