---
title: "Analysis of a dataset to compare different star classifications"
subtitle: ""
author: "Team JMAD <br> Alex, Declan, Jiayi and Malachi "
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
catalogue <- read.csv("data/hygdata_v3.csv")
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
# Load your data here
```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "img/cosmiccliffs.png"
)
```

class: center, middle


class: inverse, center, middle

# Section 1 - Introduction

---

# Our General Research Question
To investigate the relationship between different properties of stars, specifically the relationship between Spectral class and Absolute magnitude.

.pull-right[

]

---

# Our Data

Where it came from

- Kaggle Datasets - "Star dataset to predict star types". This is for the first dataset. 
- The second dataset was found in .... , it is useful as it can be mutated (there are multiple missing values) and has more variables to work with. 
--

How it was collected

- Websites & calculated by 4 Astronomical formulas

--

The cases

- 7 features about 240 stars

--

The observations and variables

- 240 observations

- Continuous discrete: Temperature(K), Luminosity(L/Lo), Radius (R/Ro), Absolute magnitude(Mv)

- Discontinuous discrete: Star type

- Categorical: Star color, Spectral Class


---

class: inverse, center, middle

# Section 2 - Data Analysis Plan


---

# Stating and Refining the Question

- 1) Descriptive: summarize the frequency for each different spectral class from a dataset based on a collection of stars.

--

- 2) Exploratory: examine relationships between a range of different properties of stars.

--

- 3) Inferential: examine whether there are any trends between star colour and luminosity.

--

- 4) Predictive: predicting the absolute magnitude based on spectral class.

--

- 5) Causal: whether a change in star radius causes a change in temperature

--

- 6) Mechanistic: how an increase in distance from the Sun causes the apparent magnitude to decrease.

---

# Plots

```{r plot-iris, echo = FALSE}

# Code hidden with echo = FALSE
# Uses modified iris dataset from previous chunk
# Play around with height and width until you're happy with the loo
acc_dist_catalogue <- catalogue %>%
   filter(distance > 0, distance < 100000) 
ggplot(acc_dist_catalogue, mapping = aes(x = absmag,
                     y = distance)) +
    labs(title = "Distance-Magnitude Relation",
              x = "Absolute Magnitude",
              y = "Distance From Earth") +
    geom_hex()


                
```

